The interactions of rational, pragmatic agents\\ lead to efficient language structure and use

### 2019-02-01 paper/paper.Rmd
update with matrix in plots according to NDG reco

```{r plot-optimal-langs, fig.env = "figure*", fig.pos = "h", fig.width=8, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages containing ambiguity. Horizontal axis shows the number of context-sizes (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only objectives. Error bars represent 95 percent confidence intervals."}
img <- png::readPNG("figs/fig1.png")
grid::grid.raster(img)
```

>>>>

```{r plot-optimal-langs, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity. Horizontal axis shows the number of context-sizes (1-4). Optimal language under CE objective (red). Speaker-optimal (blue). Listener-optimal (green). Error bars represent 95 percent confidence intervals. Panel (B), example CE-optimal language (ambiguous) under in a four-condition context. Panel (C), example CE-optimal language in a single-condition context."}
img <- png::readPNG("figs/fig1.png")
grid::grid.raster(img)
```

### 2019-02-01 paper/paper.tex
update with matrix in plots according to NDG reco

\caption[Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases]{Optimal languages are more likely to contain ambiguous items as the amount of contextual information increases. Vertical axis shows the proportion of optimal languages containing ambiguity. Horizontal axis shows the number of context-sizes (1-4). Red-line represents the optimal language under our Zipfian cross-entropy objective while the blue and red lines show optimal languages under speaker- and listener-only objectives. Error bars represent 95 percent confidence intervals.}\label{fig:plot-optimal-langs}
\end{figure*}
\end{CodeChunk}

>>>>

\caption[Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity]{Panel (A) Vertical axis shows the proportion of optimal languages containing ambiguity. Horizontal axis shows the number of context-sizes (1-4). Optimal language under CE objective (red). Speaker-optimal (blue). Listener-optimal (green). Error bars represent 95 percent confidence intervals. Panel (B), example CE-optimal language (ambiguous) under in a four-condition context. Panel (C), example CE-optimal language in a single-condition context.}\label{fig:plot-optimal-langs}
\end{figure*}
\end{CodeChunk}
